### 2017-01-10 doc/manuscript.Rmd
Included stats method for hclust of tagfa heatmap
Included/fixed QIC table

The primary outcome variables for this analysis were 1/HOMA-IR, ISI, IGI/IR, and
ISSI-2, which were log-transformed for the statistical modeling. The primary
predictor variables for this analysis were 22 individual TAGFA as mole percent
(mol%) of the total fraction and as concentration (nmol/mL). Clinically-measured
TAG is also included as a primary predictor to serve as a comparison against the
TAGFA composition. A limitation with the clinically-measured TAG is that it was
only quantified on a portion of the participants at the 6-year visit (n = `r n_tag`).
Pearson correlation coefficients were computed to assess the relationships of
individual TAGFA with other continuous variables.

@@

```{r table_qic}
table_qic_main(caption = tab_qic)
```

>>>>

The primary outcome variables for this analysis were 1/HOMA-IR, ISI, IGI/IR, and
ISSI-2, which were log-transformed for the statistical modeling. The primary
predictor variables for this analysis were 22 individual TAGFA as mole percent
(mol%) of the total fraction and as concentration (nmol/mL). Clinically-measured
TAG is also included as a primary predictor to serve as a comparison against the
TAGFA composition. A limitation with the clinically-measured TAG is that it was
only quantified on a portion of the participants at the 6-year visit (n = `r n_tag`).
Pearson correlation coefficients were computed to assess the relationships of
individual TAGFA with other continuous variables. Correlations were also
computed for TAGFA against each other, followed by using hierarchical clustering
analysis to identify clusters within the correlation matrix of the TAGFA
composition.

@@

```{r table_qic}
analyze_qic() %>% 
    table_qic(caption = tab_qic)
```
